\plaintitle

### 2016-07-25 drafts/labor/introduction.tex
more intro revisions

% %!TEX root = ./trackingWork.tex
\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

@@

\note{Is this different from other contract work? yes. here's why:}

This approach to managing work (and in particular workers)
can be differentiated from other formulations by a constellation of traits:
\begin{inlinelist}
\item distributing the workforce, % gray
\item distancing workers from the context of the work, and
\item compensating work on a per--task basis rather than for time
% citations! future of crowdwork or mary's or lily's work / quin and bederson
\end{inlinelist}.
These features can be found elsewhere
--- for instance,
distributed workforces
are a feature of global labor markets,
and abstracting workers from the products of their labor
is well--associated with
\citeauthor{marx2012economic} ---
but these components have been explored only individually
(for instance, by \citeauthor{fevre1986contract} and later \citeauthor{kalleberg2000nonstandard}),
and we focus on the newfound interest in
work arranging these components in what holistically seems to be a new mode of work
% While contract work is familiar enough,
% much of this work focuses on comprehensive work
% (for example, creative or professional work like landscaping, design, etc\dots)
\cite{kalleberg2000nonstandard,fevre1986contract,marx2012economic}.

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

@@

The many sites of work replicating
the general style of labor popularized by AMT
have predominantly involved work done on a computer
or involving the transfer of human--processed information,
leading many to refer to AMT as a site of ``information work"
\cite{turkopticon,professionalCrowdworkEthics,IraniFromCriticalDesign,OlsonMakeDistanceWorkWork}.
Still, with distributed work emerging with enough variation to problematize this description,
researchers have tried
to articulate taxonomies for the sorts of work done by many distributed workers
\cite{yuenSurvey,geiger2011managing,quinnbedersonTaxonomy}.

Attempting to triangulate the many sources of research on this area,
we offer the following takeaway:
This approach to managing work (and in particular workers)
can be differentiated from other formulations by a constellation of traits:
\begin{inlinelist}
\item distributing the workforce, % gray
\item distancing workers from the context of the work, and
\item compensating work on a per--task basis rather than for time
% citations! future of crowdwork or mary's or lily's work / quin and bederson
\end{inlinelist}.
These features can be found elsewhere
--- for instance,
distributed workforces
are a feature of global labor markets,
and abstracting workers from the products of their labor
is well--associated with
\citeauthor{marx2012economic} ---
but these components have been explored only individually
(for instance, by \citeauthor{fevre1986contract} and later \citeauthor{kalleberg2000nonstandard}),
and we focus on the newfound interest in
work arranging these components in what holistically seems to be a new mode of work
% While contract work is familiar enough,
% much of this work focuses on comprehensive work
% (for example, creative or professional work like landscaping, design, etc\dots)
\cite{kalleberg2000nonstandard,fevre1986contract,marx2012economic}.

% \note{Is this different from other contract work? yes. here's why:}
% \note{\citeauthor{quinnbedersonTaxonomy} offer a taxonomy of crowd work,
% but at a high level my takeaway consists of the following dimensions:
% This is work involving\dots
% \begin{itemize}
% \item some sort of \textbf{motivation}
% \item some sort of \textbf{quality control}
% \item some approach to \textbf{work aggregation} % this is actually kind of useful, but the wrong framing
% \item some amount of \textbf{human skill}
% \item some \textbf{process order involving a requester, a worker, and maybe a computer at various points}
% \item some notion of \textbf{task/request ``cardinality''}
% \end{itemize}
% The authors get into the dimensions that these features can take on,
% but it nevertheless seems so vague that almost any form of  work can be plotted on this 6--dimensional graph.
% }
